A GPU Implementation of Capon for an Active Sonar System

### 2012-05-03 ECUA2012/gpu_capon_ecua2012.tex
la2pdf commit - 2012:05:03	22:28:25	(Thu 3.May)

@@

By the methods just presented, we observe that for each range line, and for each sample $n$, the following steps must be carried out:
\begin{enumerate}
\item \emph{Compute the spatial covariance matrix} $\eR[n]$ (equation \ref{spatialR}-\ref{finalR}).
\item Compute $\eRi[n]\1$ (from equation \ref{weights}).
\item Substitute the solution for $\eRi[n]\1$ into equation \ref{weights} to find the weights.
\item Apply the weights to each data vector $\x_l[n]$, and sum them all up (as in equation \ref{z}) to acquire the pixel value $z[n]$.
\end{enumerate}

>>>>

CUDA...

@@

A modern \gls{GPU} is an hardware architecture comprised of several hundred computing cores, each having access to a very limited amount of local memory. This suggests that the algorithm should be decomposed into as many lightweight threads as possible, and using a single thread per pixel is not lightweight enough. Therefore, we seek to devise a clever decomposition scheme for the methods just presented. In particular, we want to distinguish between the following steps:
\begin{enumerate}
\item \emph{Computing the spatial covariance matrix} $\eR[n]$ (equation \ref{spatialR}-\ref{finalR}). In this step we launch a thread per diagonal in the upper half triangular of $\eR$, and let finished threads wrap around and start on diagonals on the lower half triangular. This way we process one row of $\eR$ at the time, and both reads and writes are kept coalesced.
\item \emph{Computing} $\eRi[n]\1$ (from equation \ref{weights}). While intuition may suggest that this step is carried out by inverting $\eR$, it is wiser to solve the linear equation $\R\beta = \1$ for $\beta$ instead, which gives us $\beta = \eRi\1$ directly. We have tested various solvers for this task, but achieved the best performance by using an unofficial batch solver from nVidia. After we optimized step 1, this remains at the most computationally intensive task.
\item \emph{Computing the subarray weights} by substituting $\eRi[n]\1$ into equation \ref{weights}.
\item \emph{Acquire the pixel value $z[n]$} by applying the weights to each data vector $\x_l[n]$, and sum them all up (as in equation \ref{z}).
\end{enumerate}

Our implementation is based on launching Since these steps have a different nature,

\subsection{Computing $\eR[n]$}
